Restaurants in Eastern Toronto More Likely to Cause Severe DineSafe Infractions

### 2024-01-25 outputs/paper/paper.qmd
Add more words about data and results and update the pdf

@@

This dataset contains 2011, 2016, and 2021 Census data and summarizes them into Toronto's 25 wards. This dataset was last refreshed on Jan 3rd, 2024, and was accessed for use on Jan 21st, 2024. We will only be using the Median household income of the wards from 2021 Census from this dataset. We decided to use 2021 Census data as it is the latest data available to us. Using older census data means we are using very recent DineSafe infraction data with misrepresented economic status of those wards.

@@

## Worst DineSafe Infraction Per Restaurant

When we obtained the DineSafe dataset (Jan 21st, 2024), there are 76,827 DineSafe inspections across 13,936 different restaurants. Of those inspections, 32,227 inspections did not have any infractions, meaning around 42% of inspections passed without minor, significant, or crucial infractions. Out of 13,936 restaurants, about 6,057 restaurants did not have any infractions, 2,816 had Minor infractions at worst, 3,872 had Significant infractions at worst, and 1,191 restaurants had crucial infractions. @tbl-restaurants-infraction-ratio shows this with the percentages compared to all restaurants. On average, there were 3.2 total infractions, 2.01 minor infractions, 1.03 significant infractions, 0.157 crucial infractions per restaurant. The standard deviation for average number of all infractions is 2.57.

@@

@@

## DineSafe Infraction and Ward Income
There doesn't seem to be a clear correlation between DineSafe Infractions and a ward's median income. This is evident looking at @tbl-income-infraction-correlation and @fig-infractions-vs-ward-income, the correlation coefficient is positive or negative depending on which severity of infraction we look at, and the data points are very spread out. Therefore the ward's median income is not a good indicator of DineSafe infraction rates.

>>>>

It is important that we use 25 ward map, not a 44 ward map that is also available on `opendatatoronto` because 25 ward map is the most commonly used ever since it came into use in 2018 [@wardsToronto1]. There is also a 47 ward model, but it is very rarely used as it was not implemented, but it is still worth mentioning because it has been approved by the city council and there are 47 wards bounds data and profile data (which is the next section) [@47wards].

@@

This dataset contains 2011, 2016, and 2021 Census data and summarizes them into Toronto's 25 wards. This dataset was last refreshed on Jan 3rd, 2024, and was accessed for use on Jan 21st, 2024. We will only be using the Median household income of the wards from 2021 Census from this dataset. We decided to use 2021 Census data as it is the latest data available to us. Using older census data means we are using very recent DineSafe infraction data with misrepresented economic status of those wards. Again, we are using 25 ward version as it is the most up to date, and most commonly used.

@@

When we obtained the DineSafe dataset (Jan 21st, 2024), there are 76,827 DineSafe inspections across 13,936 different restaurants. Of those inspections, 32,227 inspections did not have any infractions, meaning around 42% of inspections passed without minor, significant, or crucial infractions. Out of 13,936 restaurants, about 6,057 restaurants did not have any infractions, 2,816 had Minor infractions at worst, 3,872 had Significant infractions at worst, and 1,191 restaurants had crucial infractions. @tbl-restaurants-infraction-ratio shows this. On average, there were 3.2 total infractions, 2.01 minor infractions, 1.03 significant infractions, 0.157 crucial infractions per restaurant. The standard deviation for average number of all infractions is 2.57.

@@

We also observed little to no correlation between ward median houshold income and DineSafe infraction rate. This shows that perhaps DineSafe is doing a good job keeping the standard fairly even across the city. But we did observe that while wards in the central parts of the city commit the most infractions, the eastern wards seem to have the high crucial infraction rates, which are more severe, even getting close to being the highest crucial infraction rate ward. This could raise some questions as to whether this is caused by the actual physical location's properties such as climate, or outside factors such as how thorough the inspections are, and the types of establishments that are located in those areas.

@@

## DineSafe Infraction and Ward Income
There doesn't seem to be a clear correlation between DineSafe Infractions and a ward's median income. This is evident looking at @fig-infractions-vs-ward-income, the data points are very spread out, with no recognizable pattern. Therefore the ward's median income is not a good indicator of DineSafe infraction rates.
